### 2012-06-21 inst/examples/May.Rmd
May's nonlinear harvesting dynamics

`ro tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, verbose=TRUE, cache=TRUE, cache.path="criticaltransition/" or`

@@

``` {r noise}
z_g <- function() 1+(2*runif(1, 0,  1)-1) * sigma_g
````

@@

``` {r  SDP_Mat}
pdfn <- function(P, s){
  dunif(P, 1 - s, 1 + s)
}
SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g, pdfn)
````

@@

Now we'll simulate 100 replicates of this stochastic process, but with the system dynamics gradually changing over time.

``` {r simulationfunction}
Dt <- 1

ForwardSimulate <- 
  function(f, pars, x_grid, h_grid, x0, D, z_g,
         z_m=function(x) 1, z_i = function(x) 1, 
         profit=NULL){

  OptTime <- dim(D)[2]    # Stopping time
  x_h <- numeric(OptTime) # population dynamics with harvest
  h <- numeric(OptTime) # optimal havest level
  x_h[1] <- x0  # initial values
  s <- x_h # also track escapement
  x <- x_h # What would happen with no havest
  p <- numeric(OptTime)

  ## Simulate through time ##
  for(t in 1:(OptTime-1)){

    # Move towards collapse
    pars[3] <- pars[3] + Dt/OptTime

    # Assess stock, with potential measurement error
    m_t <- x_h[t] * z_m()
    # Current state (is closest to which grid posititon) 
    St <- which.min(abs(x_grid - m_t)) 
    q_t <- h_grid[D[St, (t + 1) ]] 
    # Implement harvest/(effort) based on quota with noise 
    h[t] <- q_t * z_i()
    # Noise in growth 
    z <- z_g() 
    # population grows
    x_h[t+1] <- z * f(x_h[t], h[t], pars) # with havest
    s[t+1]   <- x_h[t] - q_t # anticipated escapement
    x[t+1]   <- z * f(x[t], 0, pars) # havest-free dynamics
    p[t] <- profit(x_h[t], h[t])
  }
  data.frame(time = 1:OptTime, fishstock = x_h, harvest = h,
             unharvested = x, escapement = s, profit = p) 
}

````

The bifurcation parameter will increase from `r pars[3]` to `r pars[3] + Dt*(OptTime-1)/OptTime`.

``` {r  simulate }
sims <- lapply(1:100, function(i){
  ForwardSimulate(f, pars, x_grid, h_grid, x0=K, opt$D, z_g, z_m, z_i)
})
````

The forward simulation algorithm needs an initial condition `x0` which we set equal to the carrying capacity, as well as our population dynamics `f`, parameters `pars`, grids, and noise coefficients.  Recall in the Reed case only `z_g`, growth, is stochastic.

@@

``` {r libs2}
library(earlywarning)
````

``` {r earlywarning}
acor_tau <- dt[fishstock > 1.5, 
               warningtrend(data.frame(time=time, value=fishstock),
                            window_autocorr),
               by=reps]

var_tau <- dt[fishstock > 1.5, 
              warningtrend(data.frame(time=time, value=fishstock),
                          window_var),
              by=reps]
````

``` {r modelbased}
m <- dt[fishstock > 1.5, 
        stability_model(data.frame(time=time, value=fishstock),
                          "LSN")$pars["m"],
        by=reps]
````

``` {r summaryplot}
signals <- melt(data.frame(var=var_tau$V1, acor=acor_tau$V1, m=m$V1))
ggplot(signals) + geom_histogram(aes(value)) + facet_wrap(~variable, scales="free")
````

>>>>

`ro tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, verbose=TRUE, cache=TRUE, cache.path="May/" or`

@@

``` {r noise}
z_g <- function() rlnorm(1, 0, sigma_g)
````

@@

``` {r  SDP_Mat}
SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g)
````

@@

Now we'll simulate 100 replicates of this stochastic process,
``` {r  simulate }
sims <- lapply(1:100, function(i){
  ForwardSimulate(f, pars, x_grid, h_grid, x0=K, opt$D, z_g, z_m, z_i)
})
````

@@
